Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-31 sections/results.tex
add results for unclear

\textbf{Assurance:} In Table \ref{tb:classify_number}, there are 88\% of useful class have comments with \texttt{YES} = 2 and 3 voting scores. The classification of useless class also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores. We conjecture that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with \texttt{YES} = 1 can be useless comments. This might be an error prone from the manual assessment. To verify this, we asked practitioners to re-examined the unclear comments. We found that there are \TODO{XX}\% of 66 unclear comments changed an answer. This indicates that ......

>>>>

\textbf{Assurance:} In Table \ref{tb:classify_number}, there are 88\% of useful class have comments with \texttt{YES} = 2 and 3 voting scores. The classification of useless class also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores. We conjecture that the unclear comments with \texttt{YES} = 2 might actually be useful comments and comments with \texttt{YES} = 1 might actually be useless. The unclear result could be from error of manual assessment caused by human.
To verify this conjecture, we asked practitioners to re-examine the unclear comments.
We found that 17\% of these 66 comments became unclear because of human error.
This shows that our model \thai{what can we say about this model?}
